### 2023-09-19 3.Design/netlist.tex
Few changes
Working on netlist, to finish

\begin{itemize}
\item The first parameter is the number of input we use our system. This is the size of the input vector ($x_t$) from \cref{fig:lstmCell}.
\item The next parameter is the number of time steps. Everything about the \ac{LSTM} time steps is all explained in \cref{sec:lstm}.
\item The number of hidden state of the \ac{LSTM} network.
\item The serial size of the crossbar arrays, as described in \cref{sec:xbarCircuit}, used in the \ac{LSTM} network.
\item The files containing the weights for each part of the circuit. The weights in the files have to be organized using the following model. %TODO
\item Finally the name of the file in which the output of the script (the netlist) will be written to.
\end{itemize}

>>>>

\begin{itemize}
  \item The first parameter is the number of input we use our system. This is the size of the input vector ($x_t$) from \cref{fig:lstmCell}.
  \item The next parameter is the number of time steps. Everything about the \ac{LSTM} time steps is all explained in \cref{sec:lstm}.
  \item The number of hidden state of the \ac{LSTM} network.
  \item The serial size of the crossbar arrays, as described in \cref{sec:xbarCircuit}, used in the \ac{LSTM} network.
  \item The files containing the weights for each part of the circuit. The weights in the files have to be organized using a specific model (\cref{subsec:weiStore}).
  \item Finally the name of the file in which the output of the script (the netlist) will be written to.
\end{itemize}

\subsection{Weights storage}\label{subsec:weiStore}

The weights are stored in a single file that is the save a numpy array. The first dimension contains the weights for the different layers. Depending on the layer used, the weights are stored a bit differently :
